### 2020-06-26 Documents/ESA/sections/LitReview.tex
Restructuring of ESA

In this chapter, we explore the current state of the art in
Multi-Agent Systems (MAS). We will consider the main techniques that
have been proposed towards task allocation and control.

\fr{you might provide an overview of the introduction with the
  different sections.}

@@

\fr{I wonder whether this section would fit better in Intro.}

@@

The task of MARL is to determine an optimal joint policy for all
agents across the game. This joint policy may be the concatenation of
all the individual policy or it may just be options for each agent to
take. In either case, optimality is defined through the standard
notions of Nash equilibria and so, in this section, I will try to
consider the broad spectrum of methods which attempt to achieve
Nash equilibria. The largest problem in MARL is the non-stationarity
of the environment \cite{Hernandez-LealA}. In single-agent settings,
it is assumed that the environment is Markovian.  However, this must
be lifted in the Multi Agent setting since other agents in the
environment will be learning concurrently. As such, we must now
consider that the policy for any one agent will depend on the policy
of all other agents.

This chapter begins with a selection of the foundational methods which
were developed towards solving the MARL problem. The interested reader
may find additional methods and implementations of these techniques in
\cite{SchwartzMulti-agentApproach}.

@@

The most fundamental method to learning in Matrix games is the simplex
algorithm. This is a popular method of linear programming (in which
constraints are linear). This will be important in considering more
current methods. A similar consideration is given to the infinitesimal
gradient ascent algorithm, in which the step size converges to
zero. This method guarantees that, in the infite horizon limit, the
payoffs will converge to the Nash equilibrium payoff. Note that this
does not necessarily mean that both agents will converge to a single
Nash equilibrium. This is a particular problem in games where there
are multiple Nash equilibria. However, in practice it is difficult to
choose a convergence rate of the step size and, without an appropriate
choice the strategy may oscillate as shown in the book \fr{please add ref}. To address
this, a modified approach is presented by Bowling and Veloso which
incorporates the notion of Win or Learn Fast (WoLF) to produce
WoLF-IGA \cite{Bowling2002}.  WoLF is a notion we will come across
often in MARL and is shown by the authors to converge to always to a
NE. The concern with WoLF methods, however, is that it requires
explicit knowledge of the payoff matrix (which is not so much of a
problem for model based methods) and the opponent's strategy (which is
more of a problem in real-world methods). Finally, the Policy Hill
Climbing method (PHC) is shown to converge to an optimal mixed
strategy if the other agents are stationary (i.e.~are not
learning). However, it is shown that, when this is not the case, the
algorithm again oscillates. The WoLF-PHC adaptation of this method is
shown to converge to a NE strategy for both players with minimal
oscillation.

@@

Stochastic Games (or Markov Games) form a basis for MARL
settings. However, in this case the agents must learn about the
equilibrium strategies by playing the game, which means they do not
have a priori knowledge of the reward or transition functions. Schwarz
considers \fr{where?} two properties which should be used for evaluating MARL
algorithm: rationality and convergence. The latter simply states that
the method should converge to some equilibrium whereas the former
suggests that the method should learn the best response to stationary
opponents. A similar set of conditions is considered by Conitzer and
Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
shortly. Schwarz then presents a review of MARL methods (as of
September 2014)

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al. show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that the authors have identified this problem and are currently working towards its incorporation into the
model.

@@

\fr{I really liked this section.}

@@

\fr{\textbf{what about some use cases/application scenarios.}}

>>>>

\textbf{TODO: Mention the parts of literature which we are not considering and explain why: Recent
MARL techniques (including MDRL), Marco Dorigo's work on Swarms. Add in the Learning in Stochastic
Games literature from Schwartz et al. Explain the concepts in Control Theory and how MPC works. Add
in suggestions for applications and papers supporting said applications.}

In this chapter, we explore the current state of the art in
Multi-Agent Systems (MAS). We will consider the main techniques that
have been proposed towards task allocation and control. In this review we cover

\begin{enumerate}
    \item Game Theory: The most well studied model for solving multi-agent decision making problems.
    \item Multi-Agent Reinforcement Learning (MARL): A contemporary technique which requires that
    agents learn and adopt their own strategies.
    \item Control Theory: Methods focusing on low-level manipulation of a system (e.g. the position
    and velocity of an agent) which aims to provide guarantees on its behaviour.
    \item Swarms: Systems whose success are founded on the emergent phenomena exhibited by large
    populations of interacting entities.
\end{enumerate}

There are, of course, a number of techniques which we do not discuss here, as they are not relevant
to the proposals in this report. Most notable is that of Decentralised Partially Observable Markov
Decision Processes (Dec-POMDPs) which is a multi-agent extension of the MDP framework in which
agents aim to maximise a common reward (or utility) function. This method does not scale to large
populations and so is not considered relevant to our study. The interested reader should consult
\cite{OliehoekDecentralizedPOMDPs} for an excellent introduction to Dec-POMDPs.

@@

@@

The task of MARL is to determine an optimal joint policy for all
agents across the game. This joint policy may be the concatenation of
all the individual policy or it may just be options for each agent to
take. In either case, optimality is defined through the standard
notions of Nash equilibria and so, in this section we
consider the broad spectrum of methods which attempt to achieve
Nash equilibria.

The largest problem in MARL is the non-stationarity
of the environment \cite{Hernandez-LealA}. In single-agent settings,
it is assumed that the environment is Markovian.  However, this must
be lifted in the Multi Agent setting since other agents in the
environment will be learning concurrently. As such, we must now
consider that the policy for any one agent will depend on the policy
of all other agents.

This section begins with a selection of the foundational methods which
were developed towards solving the MARL problem. The interested reader
may find additional methods and implementations of these techniques in
\cite{SchwartzMulti-agentApproach}.

@@

The most fundamental method to learning in Matrix games is the simplex
algorithm. This is a popular method of linear programming (in which
constraints are linear). This will be important in considering more
current methods. A similar consideration is given to the infinitesimal
gradient ascent algorithm, in which the step size converges to
zero. This method guarantees that, in the infite horizon limit, the
payoffs will converge to the Nash equilibrium payoff. Note that this
does not necessarily mean that both agents will converge to a single
Nash equilibrium. This is a particular problem in games where there
are multiple Nash equilibria. However, in practice it is difficult to
choose a convergence rate of the step size and, without an appropriate
choice the strategy may oscillate as shown in the book \cite{SchwartzMulti-agentApproach}. To
address
this, a modified approach is presented by Bowling and Veloso which
incorporates the notion of Win or Learn Fast (WoLF) to produce
WoLF-IGA \cite{Bowling2002}.  WoLF is a notion we will come across
often in MARL and is shown by the authors to converge to always to a
NE. The concern with WoLF methods, however, is that it requires
explicit knowledge of the payoff matrix (which is not so much of a
problem for model based methods) and the opponent's strategy (which is
more of a problem in real-world methods). Finally, the Policy Hill
Climbing method (PHC) is shown to converge to an optimal mixed
strategy if the other agents are stationary (i.e.~are not
learning). However, it is shown that, when this is not the case, the
algorithm again oscillates. The WoLF-PHC adaptation of this method is
shown to converge to a NE strategy for both players with minimal
oscillation.

@@

Stochastic Games (or Markov Games) form a basis for MARL
settings. However, in this case the agents must learn about the
equilibrium strategies by playing the game, which means they do not
have a priori knowledge of the reward or transition functions. Schwarz \cite{SchwartzMulti-agentApproach}
considers two properties which should be used for evaluating MARL
algorithm: rationality and convergence. The latter simply states that
the method should converge to some equilibrium whereas the former
suggests that the method should learn the best response to stationary
opponents. A similar set of conditions is considered by Conitzer and
Sandholm in \cite{ConitzerAWESOME:}. Schwarz then presents a review of MARL methods (as of
September 2014).

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al. show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that the
authors of \cite{Inoue2019} have identified this problem and are currently working towards its
incorporation into the model.

@@

@@

### 2020-06-26 Documents/ESA/sections/ProposedResearch.tex
Restructuring of ESA

	This chapter describes a proposed line of research which aims
        to study the evolution of swarm systems with independent,
        learning agents under the influence of predictive controls. We
        detail the novel lines of research which this work aims to
        undertake, providing suggestions of the hypotheses posed by
        these lines. With this in mind the following studies are
        proposed and developed subsequently:

	\begin{itemize}
		\item \textbf{Stability and Chaos in MARL:} in which
                  we seek to understand the dynamics of agent
                  strategies when using Q-Learning to learn a game
                  through iteration. We will establish the stability,
                  as a function of parameters, when learning general
                  p-player N-action games.  This study enables the
                  appropriate selection of parameters and payoff
                  matrices to ensure the stability of the strategies
                  of a finite set of agents, such as leaders in a
                  swarm.

                  \fr{this is already attempted in the current
                    research section, isn't it?}

              \item \textbf{Dynamics of Mean-Field Q-Learning Games:} in which we examine the
		strategy dynamics for large populations of agents learning through iterated games and
		mean-field Q-Learning. We seek to understand the long term behaviour of such mean-field
		systems in terms of its strategy selection. This study extends the previous and allows for
		the stability of the strategies of a population of agents to be established.
		\item \textbf{Model Predictive Control of Active Particles through Fields:} in which we
		investigate the interaction of a swarm of active particles with potential fields. We
		establish the stabilisability of an MPC scheme with defined stage costs, as well as an
		analysis of the suboptimality of the method.
		\item \textbf{Incorporation of Intelligence in Control:} in which we adapt the dynamical
		system from the above point to include an interaction term, accounting for strategy
		selection by agents who learn through iterated games against one another. Interactions with
		an MPC scheme is then to be examined in a similar capacity.

	\end{itemize}

	The remainder of this chapter analyses each of these topics in turn, providing suggestions for
	the course of research.
        \fr{we analyze each topic in a section \ldots}

@@

    \section{Stability and Chaos in MARL} \label{sec::Chaos_in_MARL}

    This segment of research is aimed towards a deeper understanding
    of the strategy evolution of agents following a Q-Learning
    approach. This allows for guarantees to be placed on the behaviour
    of such agents, in particular the conditions under which the game
    will converge to a stable equilibrium.

    It has long been established that, upon lifting the strong
    assumptions made by traditional game theory (such as the
    rationality of agents and complete information), that player
    strategies can result in much more complex behaviour than
    convergence to a Nash Equilibrium (NE). In fact, this is even true
    on what would commonly be regarded as 'simple' games such as
    tic-tac-toe and prisoner's dilemma \cite{Galla2011,
      Sato2002}. These behaviours include: convergence to a unique
    equilibrium (though not always to an NE), convergence to one of
    multiple equilibria, limit cycles and chaos. These behaviours are
    shown in Figure \ref{fig::DynamicalBehaviours} Of these, the most
    preferable is, of course, convergence to a unique equilibrium,
    although it is still possible to study systems with multiple
    equilibria or limit cycles \cite{Strogatz2000}. However, it would
    be difficult to control systems whose dynamics are governed by
    chaos (though research into controlling chaos is ongoing and rife
    with opportunity \cite{Fradkov2009}) and so MARL techniques should
    avoid this. It would, therefore, be a useful endeavour to
    determine the conditions under which these sorts of behaviours
    arise.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
       displayed
    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
    	Convergence
    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
    	exponentially. b-d drawn from \cite{Sanders2018}}
    \end{figure}

    The behaviour of a system may be studied given a model of its
    dynamics. It is through this process that a wide array of physical
    systems, from harmonic pendulums to geophysical fluids, can be
    understood. A growing body of research aims to understand
    multi-agent reinforcement learning through the lens of its
    dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames} were
    able to derive a model of the strategy evolution of agents
    learning through iterated games.  Through this, they were able to
    arrive at the following model of Multi-Agent Q-Learning

	\begin{subequations}
	\label{eqn::EOM}
		\begin{equation}
			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
		\end{equation}
	\end{subequations}

\fr{I understand the equations are the same as in the previous section. I suggest we move the explanation there and remove it from here.}

	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
	memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
	$x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
	predict the expected behaviour of Q-Learning agents, as shown in Figure 
	\ref{fig::TuylsExperiments}.

	\begin{figure}[h]
		\centering
		\begin{subfigure}[b]{0.9 \textwidth}
			\centering
			\includegraphics[width=0.75 \textwidth]{Figures/Dynamics}
			\caption{}
		\end{subfigure}

		\begin{subfigure}[b]{0.9 \textwidth}
			\centering
			\includegraphics[width=0.7 \textwidth]{Figures/Q-Learners}
			\caption{}
		\end{subfigure}

		\caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
		plot showing the expected behaviour of Q-Learning agents trained by iterating the
		Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
		have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
		randomised initial conditions displayed through numerical simulation. It is clear that the
		trajectories in b) follow the predictions in a), after stochasticity is accounted for. }
	\end{figure}

	It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments} that the long-term strategy selection of
	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
	then pose the question: how do these elements influence the types of behaviours seen during
	learning on an iterated game? In other words, under what parameter selections are we likely to
	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?

	With this in mind, the intention of this area of study is to consider the analysis presented in
	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
	determine the regions of parameter space in which complex behaviour,
	including cycles and chaos, predominantly occur and those in which a given game converges to a
	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
	illustrates the successful derivation of a `phase line', across which learning shifts from
	convergent to chaotic.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.6\textwidth]{Figures/GallaPredictions}
    	\caption{ \label{fig::GallaPredictions} Results as produced in the supplementary material
    	of Sanders et al \cite{Sanders2018}. Here, $p$ is the number of players, $N$ is the number
    	of actions, $\Gamma$ represents the competitiveness of the game (-1 represents zero-sum, 1
    	represents shared rewards) and $\alpha$ is the memory parameter of the agent as before.
    	Here $\tau$ is held constant at 0.05 (though it is referred to as $\beta$ in the paper).
    	The black region represents where games converged to a fixed point through all simulations,
    	whilst the hotter regions represent the more complex dynamics - red shows the presence of
    	limit cycles and white regions signal the onset of chaos. The green line is a theoretical
    	estimation for the phase line which separates the convergent dynamics from complex.}
    \end{figure}

    We propose to bridge the analysis presented by Sanders
    et al. and Galla et al. towards games learnt using MARL, particularly Q-Learning with
    Boltzmann exploration as considered by Tuyls et al. This would allow for a characterisation of
    the expected resultant behaviour under given parameters for a particular game. The vision for
    this is to provide guarantees on the stability of a finite set of agents within a swarm, such as
    leaders in a flock. Without this, it would be impossible to ensure the stability of a swarm in
    which intelligent, social interactions must be accounted for. However, this analysis
    would also allow for a characterisation of the conditions under which MARL algorithms may
    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
    payoff matrices and parameters accordingly.

    This segment of research is currently underway and approaching completion. The analysis was
    described in Section \ref{sec::Chaos_in_Q-Learning}.

    \fr{I would move all of the above to the previous section.}

@@

    One of the main results shown by Sanders et al. \cite{Sanders2018}
    is that as the number of players in a game increases, the learning
    behaviour is more likely to be chaotic, regardless of the choice
    of parameters. This is intuitive since a higher number of players
    would result in a greater strategy space and more agents for any
    particular player to learn against and is verified by their
    presented results as in Figure \ref{fig::GallaPrevalence} - the
    hotter regions occupy a larger area as \fr{?}

@@

    Yet it can be argued that, for large populations of agents (e.g.,
    a crowd), the aggregate behaviour may be predictable \fr{provide some justification to this claim?}. This
    intuition is the foundation upon which crowd dynamics and flocking
    systems are based. In fact, the work presented by Leung et
    al.~\cite{Hu2019} provides a cursory verification of this
    intuition. Here, the authors present an analysis of the learning
    dynamics for a large agent population (which they approximate as
    containing infinite agents) where each agent is an independent
    Q-Learning using Boltzmann action selection. The result is a
    system of equations, governed by a Fokker-Planck model which is
    numerical shown to be a strong predictor of the overall strategy
    selection of the population. Indeed, rather than examining the
    strategies of every agent in the population (which the authors
    approximate as infinitely large), they model the evolution of a
    probability density function which, for each action, defines the
    density of agents who retain a given Q-value for that action. This
    is illustrated in Figure \ref{fig::LeungPredictions}.

@@

	\begin{itemize}
		\item Estimate the population state through Random Finite Sets (RFS) and
	apply the models from the previous study. The aim here is to determine a state
	estimation for a swarm of unknown size through a random finite set by solving
	an optimal estimation problem  (typically iterated through a Kalman Filter
	\cite{Doerr2019}. As the swarm is treated probailistically, the theory can
	accomodate an arbitrarily large system. Importantly, this may allow for the
	results from the previous section to be leveraged towards an arbitrary
	population.

@@

    Here we aim to study the interaction of a swarm of 'active particles' with a potential field. In
    particular this field is to be generated by 'field particles'. A model predictive control 
    (MPC) scheme
    is to be devised to drive this system to desired configurations, with guarantees placed on
    stability and satisfaction of input constraints. The sub-optimality of the control
    scheme is to be studied.

    As described in Chapter \ref{ch::Lit_Review}, the control of swarms has been examined through the
    use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
    Roy2017}, though it makes the assumption that the system evolves through 'drifted
    brownian motion'. This means that the agents are considered to move about independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Fleig}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{Burger2019}.

	The hypothesis of this section is that the distribution of active particles, whose evolution is
	described through a Vlasov equation, may be controlled through the influence of a scalar field
	generated by 'field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
	\cite{Bellomo2017}

@@

    Here, $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$ which represents the state of
    the system. $\kappa \geq 0$ is a scalar
    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
    {v}^*$) gives the position in phase space of a 'field particle'. It can be seen that the these
    field particles influence the velocity of the swarm agents.

@@

    This section of the study is perhaps the strongest extension
    proposed in this chapter, and will likely be the most
    challenging. Here, we examine the dynamics (\ref{eqn::Vlasov}) in
    which the interaction term accounts for the social dynamics of the
    decision making of individual agents who have learnt through an
    iterated game. We leverage the strategy evolution dynamics and
    stability analysis established in \ref{sec::Chaos_in_MARL} and
    \ref{sec::Large_Agent_Dynamics}.

>>>>

    This chapter continues to describe the proposed research outined in Chapter 
    \ref{ch::IntrotoProposals}. These proposals are to be addressed following the completion of the
    research in Chapter \ref{ch::ShortTermGoals}.

@@

@@

    One of the main results shown by Sanders et al. \cite{Sanders2018}
    is that as the number of players in a game increases, the learning
    behaviour is more likely to be chaotic, regardless of the choice
    of parameters. This is intuitive since a higher number of players
    would result in a greater strategy space and more agents for any
    particular player to learn against and is verified by their
    presented results as in Figure \ref{fig::GallaPrevalence} - the
    hotter regions occupy a larger area as $p$ increases.

@@

    Yet it can be argued that, for large populations of agents (e.g.,
    a crowd), the aggregate behaviour may be predictable, since the individual effect on the overall
    population is negligible \cite{Elamvazhuthi2019b}. This
    intuition is the foundation upon which crowd dynamics and flocking
    systems are based. In fact, the work presented by Leung et
    al. \cite{Hu2019} provides a cursory verification of this
    intuition. Here, the authors present an analysis of the learning
    dynamics for a large agent population (which they approximate as
    containing infinite agents) where each agent is an independent
    Q-Learning using Boltzmann action selection. The result is a
    system of equations, governed by a Fokker-Planck model which is
    numerically shown to be a strong predictor of the overall strategy
    selection of the population. Indeed, rather than examining the
    strategies of every agent in the population (which the authors
    approximate as infinitely large), they model the evolution of a
    probability density function which, for each action, defines the
    density of agents who retain a given Q-value for that action. This
    is illustrated in Figure \ref{fig::LeungPredictions}.

@@

	\begin{itemize}
		\item Estimate the population state through Random Finite Sets (RFS) and
	apply the models from the previous study. The aim here is to determine a state
	estimation for a swarm of unknown size through a random finite set by solving
	an optimal estimation problem  (typically iterated through a Kalman Filter
	\cite{Doerr2019}. As the swarm is treated probabilistically, the theory can
	accomodate an arbitrarily large system. Importantly, this may allow for the
	results from the previous section to be leveraged towards an arbitrary
	population.

@@

    Here we aim to study the interaction of a swarm of `active particles' with a potential field.
    In
    particular this field is to be generated by `field particles'. A Model Predictive Control 
    (MPC) scheme
    is to be devised to drive this system to desired configurations, with guarantees placed on
    stability and satisfaction of input constraints. The sub-optimality of the control
    scheme is to be studied.

    As described in Chapter \ref{ch::Lit_Review}, the control of swarms has been examined through the
    use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
    Roy2017}, though it makes the assumption that the system evolves through `drifted
    brownian motion'. This means that the agents are considered to move independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Fleig}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{Burger2019}.

	The hypothesis of this section is that the distribution of active particles, whose evolution is
	described through a Vlasov equation, may be controlled through the influence of a scalar field
	generated by `field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
	\cite{Bellomo2017}

@@

    Here, $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$ which represents the state of
    the system. $\kappa \geq 0$ is a scalar
    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
    {v}^*$) gives the position in phase space of a `field particle'. It can be seen that the these
    field particles influence the velocity of the swarm agents.

@@

    This section of the study is perhaps the strongest extension
    proposed in this chapter, and will likely be the most
    challenging. Here, we examine the dynamics (\ref{eqn::Vlasov}) in
    which the interaction term accounts for the social dynamics of the
    decision making of individual agents who have learnt through an
    iterated game. We leverage the strategy evolution dynamics and
    stability analysis established in \ref{ch::ShortTermGoals} and
    \ref{sec::Large_Agent_Dynamics}.
